Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
check consistency

	\begin{figure*} 	
		\includegraphics[width=0.3\textwidth]{fig4/task1-scalar-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/task3-scalar-lstm.pdf}
		%\vspace{-20pt}  
		\caption{Relative prediction errors for $R_r(t)$ and $avgRTT_P(t)$ of LSTM models with scalar input.}
		\label{fig:task1_LSTM_SC}
		%\vspace{-10pt}  
	\end{figure*}

@@

	Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it. \textbf{Fig.\ref{fig:task1_LSTM_SC}} and \textbf{Tab.\ref{tab:lstm-scalar}} show the results.

@@

	To the contrast, for target $avgRTT_P(t)$, the $ABC$ of LSTM is lower than random forest in all cases, which may indicates that $avgRTT_P(t)$ is less likely to have the temporal locality.

	For both tasks, use scalar input for LSTM cannot outperform random forest steadily.

	\subsubsection{Vector Input}
	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM as random forest. More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
	\begin{table}[t]
		\centering
		\begin{tabular}{lcc}
			\toprule
			{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
			\midrule
			\textit{data-1}& 0.5374 & 0.7310 \\
			\textit{data-2}& 0.4956& 0.7039     \\
			\textit{data-3-ws10}& 0.7649 & 0.7521 \\
			\textit{data-3-ws20}& 0.6513& 0.6901    \\
			\textit{data-3-ws50}& 0.5647& 0.7074  \\
			\bottomrule	
		\end{tabular}
		\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
		\label{tab:lstm-vector}
	\end{table}

	In general, the results is consist with our previous observation that $R_r(t)$ has more temporal locality while $avgRTT_p(t)$ seems has few or no temporal locality.

	More specificly, for target $R_r(t)$, LSTM outperforms random forest in all the 5 data set with a maximum $ABC=0.7649$. And when fed with vector input, the LSTM has a significant lift in performance than LSTM with scalar input, which shows that high quality features can be benefit to not only classic shadow models like random forest, but also \textit{deep} models.

	However, when it comes to target $avgRTT_p(t)$, although LSTM does has better performance when fed with vector input rather than scalar input, its $ABC$ is still lower than random forest's. We believe it is because there is less temporal locality with $avgRTT_p(t)$. The more data you observed before, the better you can predict $avgRTT_p(t)$ in the future. Thus LSTM model cannot maximize its ability in predicting temporal patterns.
	\section{Conclusions}
	TODO

>>>>

	\begin{figure*} 	
		\includegraphics[width=0.3\textwidth]{fig4/task1-scalar-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/task3-scalar-lstm.pdf}
		%\vspace{-20pt}  
		\caption{Relative prediction errors for $R_r(t)$ and $avgRTT_P(t)$ of LSTM models with scalar input.}
		\label{fig:lstm_scalar}
		%\vspace{-10pt}  
	\end{figure*}

@@

	Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it. \textbf{Fig.\ref{fig:lstm_scalar}} and \textbf{Tab.\ref{tab:lstm-scalar}} show the results.

@@

	By contrast, for target $avgRTT_P(t)$, the $ABC$ of LSTM is smaller than random forest in all cases, which may indicate that $avgRTT_P(t)$ is less likely to have the temporal locality.

	For both tasks, using scalar input for LSTM cannot outperform random forest steadily.

	\subsubsection{Vector Input}
	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM model as those for random forest model. More specifically, Features for target $R_r(t)$ and Features for target $avgRTT_P(t)$.The results are shown in \textbf{Fig.\ref{fig:lstm-task1-vector}}, \textbf{Fig.\ref{fig:lstm-task3-vector}} and \textbf{Tab.\ref{tab:lstm-vector}}.

	\begin{figure*} 	
		\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-1-7030-lstm.pdf}
		%\vspace{-20pt}  
		\caption{Relative prediction errors for $R_r(t)$ of LSTM models with vector input.}
		\label{fig:lstm-task1-vector}
		%\vspace{-10pt}  
	\end{figure*}
	\begin{figure*} 	
	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-3-7030-lstm.pdf}
	%\vspace{-20pt}  
	\caption{Relative prediction errors for  $avgRTT_P(t)$ of LSTM models with vector input.}
	\label{fig:lstm-task3-vector}
	%\vspace{-10pt}  
	\end{figure*}
	\begin{table}[t]
		\centering
		\begin{tabular}{lcc}
			\toprule
			{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
			\midrule
			\textit{data-1}& 0.5374 & 0.7310 \\
			\textit{data-2}& 0.4956& 0.7039     \\
			\textit{data-3-ws10}& 0.7649 & 0.7521 \\
			\textit{data-3-ws20}& 0.6513& 0.6901    \\
			\textit{data-3-ws50}& 0.5647& 0.7074  \\
			\bottomrule	
		\end{tabular}
		\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
		\label{tab:lstm-vector}
	\end{table}

	In general, the results consist with our previous observation that $R_r(t)$ has more temporal locality while $avgRTT_p(t)$ seems to have less or no temporal locality.

	More specifically, for target $R_r(t)$, LSTM model outperforms random forest model in all five data processing manners with a maximum $ABC=0.7649$. And when fed with vector input, the LSTM has a significant lift in performance than LSTM with scalar input, which shows that high quality features can be beneficial to not only classic shadow models like random forest, but also \textit{deep} models like LSTM model.

	However, when it comes to target $avgRTT_p(t)$, although LSTM models do have better performance when fed with vector input rather than scalar input, their $ABC$s are still smaller than those of random forest. We believe it is because there is less temporal locality with reference to $avgRTT_p(t)$. The more data we observed before, the better we can predict $avgRTT_p(t)$ in the future. Thus LSTM model cannot maximize its ability in predicting temporal patterns.
	\section{Conclusions}
	TODO
